Open Data

### 2020-09-25 draft_chapter.Rmd
re-knit pdf and word

---
title: "Open Data"
date: "June 2020"
editor_options:
  chunk_output_type: console
output:
  word_document: default
  pdf_document:
    latex_engine: xelatex
bibliography: refs.bib
---

>>>>

---
title: "Open Data"
date: "June 2020"
editor_options:
  chunk_output_type: console
output:
  pdf_document:
    latex_engine: xelatex
  word_document: default
bibliography: refs.bib
---
